msc dissertation

### 2021-07-19 msc dissertation code.Rmd
latest

pennycook1 <- read_csv("Pennycook et al._Study 1.csv")
Pennycook2 <- read_csv("Pennycook et al._Study 2.csv")

@@

>>>>

pennycook1 <- read_csv("Pennycook et al._Study 1.csv")
pennycook2 <- read_csv("Pennycook et al._Study 2.csv")
# Quick check
head(pennycook2)

@@

# General steps to regenerate headline result (study 2)
## data cleaning

# rename columns that contains special characters
colnames(pennycook2)
names(pennycook2)[1] <- "condition"

#conclude a sheet with only the relevant information 
#condition 1 = control; condition 2 = treatment

#Choose with the column position 
library("dplyr")
pennystudy2r1 <- pennycook2 %>% 
  select (c(1, 2, 3, 4, 57, 60, 250, 252, 284))

#re-code sharing intentions (fake/real) using the scale midpoint (1-3 = 0, 4-6 = 1)
pennystudy2r1$Fake[pennystudy2r1$Fake > 0 & pennystudy2r1$Fake < 4] <- 0
pennystudy2r1$Fake[pennystudy2r1$Fake > 3 & pennystudy2r1$Fake < 7] <- 1
pennystudy2r1$Fake

pennystudy2r1$Real[pennystudy2r1$Real > 0 & pennystudy2r1$Real < 4] <- 0
pennystudy2r1$Real[pennystudy2r1$Real > 3 & pennystudy2r1$Real < 7] <- 1
pennystudy2r1$Real

```
## reproduction of results (interaction between headline veracity and treatment)
### without considering attention check
```{r, message=FALSE}

lm1 = lm(Discern ~ condition, data = pennystudy2r1)
summary(lm1)

### reproduction of figure 2 without considering attention check

```{r, message=FALSE}
pennystudy2r1$screen3_2

library(ggplot2)

pennystudy2plot1 <- pennystudy2r1 %>% 
  select (c(1, 2, 3))

library(reshape2)

pennystudy2plot1 <- melt(pennystudy2plot1, id = 'condition')
head(pennystudy2plot1)

#Find out the sum for each type of news in different condition
p1 <- aggregate(value~condition+variable, data = pennystudy2plot1, FUN = sum)

ggplot(p1, aes(x = condition, y = value / 428, fill = variable)) + 
  geom_bar(stat = 'identity',position = 'dodge')
